%\cite{Belitsky:2005qn}
\bibitem{Mueller:1998fv} 
  D.~Müller, D.~Robaschik, B.~Geyer, F.-M.~Dittes and J.~Hořejši,
  %``Wave functions, evolution equations and evolution kernels from light ray operators of QCD,''
  Fortsch.\ Phys.\  {\bf 42}, 101 (1994)
  [hep-ph/9812448].
  %%CITATION = HEP-PH/9812448;%%
  %891 citations counted in INSPIRE as of 24 Apr 2015
\bibitem{Ji97-1}
X.~Ji, Phys.\ Rev.\ Lett.\ {\bf 78}, 610 (1997).

%\cite{Ji:1996nm}
\bibitem{Ji97-2} 
  X.~-D.~Ji,
  ``Deeply virtual Compton scattering,''
  Phys.\ Rev.\ D {\bf 55}, 7114 (1997)
  [hep-ph/9609381].
  %%CITATION = HEP-PH/9609381;%%
  %833 citations counted in INSPIRE as of 14 Nov 2013

\bibitem{Rad97}
A.V.~Radyushkin, Phys.\ Rev.\ {\bf D 56}, 5524 (1997).
 
 \bibitem{Die03}
M.~Diehl, Phys.\ Rep.\ {\bf 388}, 41 (2003).

\bibitem{Bel05} 
  A.~V.~Belitsky and A.~V.~Radyushkin,
  ``Unraveling hadron structure with generalized parton distributions,''
  Phys.\ Rept.\  {\bf 418}, 1 (2005)
  [hep-ph/0504030].
  %%CITATION = HEP-PH/0504030;%%
  %425 citations counted in INSPIRE as of 14 Nov 2013
  
\bibitem{Gui03} 
  M.~Guidal and M.~Vanderhaeghen,
  ``Generalized Parton Distributions in the valence region from Deeply Virtual Compton Scattering'',
  [arXiv:1303.6600v3].
     
\bibitem{Belitsky:2001ns}
  Belitsky A V, Mueller D and Kirchner A 2002
  Theory of deeply virtual Compton scattering on the nucleon 
  {\it Nucl.\ Phys.\  B} {\bf 629} 323  
  %[arXiv:hep-ph/0112108].
  %%CITATION = NUPHA,B629,323;%%

  
  \bibitem{halla:e12-06-114} 
  Approved Hall A experiment E12-06-114,
  ``Measurements of Electron-Helicity Dependent Cross Sections of Deeply Virtual Compton Scattering with CEBAF at 12 GeV'',\\
$http://www.jlab.org/exp\_prog/PACpage/PAC38/proposals/Previously\_Approved/E12-06-114\_Update.pdf$
      
  \bibitem{clas12:e12-06-119} 
  Approved CLAS12 experiment E12-06-119,
  ``Deeply Virtual Compton Scattering with CLAS12 at 11 GeV'',\\
$http://www.jlab.org/exp\_prog/PACpage/PAC38/proposals/Previously\_Approved/E12-06-119\_Update.pdf$
  
     \bibitem{clas12:e12-11-003} 
  Approved CLAS12 experiment E12-11-003,
  ``Deeply Virtual Compton Scattering on the Neutron with CLAS12 at 11 GeV'',\\
$http://www.jlab.org/exp\_prog/PACpage/PAC38/proposals/Previously\_Approved/E12-11-003\_Update.pdf$

%\cite{Guidal:2002kt}
\bibitem{vgg} 
  Vanderhaeghen M, Guichon P A M and Guidal M 1999
  Deeply virtual electroproduction of photons and mesons on the nucleon: Leading order amplitudes and power corrections 
  {\it Phys.\ Rev.\ D} {\bf 60} 094017 
  %[hep-ph/9905372].
  %%CITATION = HEP-PH/9905372;%%

%\cite{Collaboration:2010kna}
\bibitem{Collaboration:2010kna} 
  E.~Fuchey, A.~Camsonne, C.~Munoz Camacho, M.~Mazouz, G.~Gavalian, E.~Kuchina, M.~Amarian and K.~A.~Aniol {\it et al.},
  ``Exclusive Neutral Pion Electroproduction in the Deeply Virtual Regime,''
  Phys.\ Rev.\ C {\bf 83}, 025201 (2011)
  [arXiv:1003.2938 [nucl-ex]].
  %%CITATION = ARXIV:1003.2938;%%
  %14 citations counted in INSPIRE as of 14 Nov 2013

%\cite{Munoz Camacho:2006hx}
\bibitem{MunozCamacho:2006hx} 
  C.~M.~ño.~Camacho {\it et al.}  [Jefferson Lab Hall A and Hall A DVCS Collaborations],
  ``Scaling tests of the cross-section for deeply virtual compton scattering,''
  Phys.\ Rev.\ Lett.\  {\bf 97}, 262002 (2006)
  [nucl-ex/0607029].
  %%CITATION = NUCL-EX/0607029;%%
  %140 citations counted in INSPIRE as of 14 Nov 2013

\bibitem{PhysRevLett.100.162002} 
  F.X. Girod {\it et al.}  [CLAS Collaborations],
  Deeply Virtual Compton Scattering Beam-Spin Asymmetries``,
  Phys.\ Rev.\ Lett.\ {\bf100}, 162002 (2008)
  [arXiv:0711.4805 [nucl-ex]].
  %%CITATION = NUCL-EX/0607029;%%
  %140 citations counted in INSPIRE as of 14 Nov 2013

%\cite{Mazouz:2007aa}
\bibitem{Mazouz:2007aa} 
  M.~Mazouz {\it et al.}  [Jefferson Lab Hall A Collaboration],
  ``Deeply virtual compton scattering off the neutron,''
  Phys.\ Rev.\ Lett.\  {\bf 99}, 242501 (2007)
  [arXiv:0709.0450 [nucl-ex]].
  %%CITATION = ARXIV:0709.0450;%%
  %79 citations counted in INSPIRE as of 14 Nov 2013
%\cite{Mazouz:2007aa}

 \bibitem{Airapetian:2001yk}
  Airapetian A {\it et al.}  [HERMES Collaboration] 2001
  Measurement of the beam spin azimuthal asymmetry associated with
  deeply-virtual Compton scattering
  {\it Phys.\ Rev.\ Lett.}  {\bf 87}, 182001
  %[arXiv:hep-ex/0106068].
  %%CITATION = PRLTA,87,182001;%%

\bibitem{Airapetian:2012mq} 
  Airapetian A {\it et al.}  [HERMES Collaboration] 2012
  Beam-helicity and beam-charge asymmetries associated with deeply virtual Compton scattering on the unpolarised proton
  {\it JHEP} {\bf 1207}, 032
  %[arXiv:1203.6287 [hep-ex]].
  %%CITATION = ARXIV:1203.6287;%%

\bibitem{Airapetian:2010ab} 
  Airapetian A {\it et al.}  [HERMES Collaboration] 2010
  Exclusive Leptoproduction of Real Photons on a Longitudinally Polarised Hydrogen Target
  {\it JHEP} {\bf 1006}, 019
  %[arXiv:1004.0177 [hep-ex]].
  %%CITATION = ARXIV:1004.0177;%%

\bibitem{Airapetian:2008aa} 
  Airapetian A {\it et al.}  [HERMES Collaboration] 2008
  Measurement of Azimuthal Asymmetries With Respect To Both Beam Charge and Transverse Target Polarization in Exclusive Electroproduction of Real Photons
  {\it JHEP} {\bf 0806}, 066
  %[arXiv:0802.2499 [hep-ex]].
  %%CITATION = ARXIV:0802.2499;%%

\bibitem{Airapetian:2011uq} 
  Airapetian A {\it et al.}  [HERMES Collaboration] 2011
  Measurement of double-spin asymmetries associated with deeply virtual Compton scattering on a transversely polarized hydrogen target
  {\it Phys.\ Lett.\ B} {\bf 704}, 15
  %[arXiv:1106.2990 [hep-ex]].
  %%CITATION = ARXIV:1106.2990;%%

\bibitem{Airapetian:2006zr}
  Airapetian A {\it et al.}  [HERMES Collaboration] 2007
  The beam-charge azimuthal asymmetry and deeply virtual Compton
  scattering
  {\it Phys.\ Rev.\  D} {\bf 75}, 011103 
  %[arXiv:hep-ex/0605108].
  %%CITATION = PHRVA,D75,011103;%%
%\cite{Airapetian:2009aa}

\bibitem{Airapetian:2009aa} 
  Airapetian A {\it et al.}  [HERMES Collaboration] 2009
  Separation of contributions from deeply virtual Compton scattering and its interference with the Bethe-Heitler process in measurements on a hydrogen target
  {\it JHEP} {\bf 0911}, 083
  %[arXiv:0909.3587 [hep-ex]].
  %%CITATION = ARXIV:0909.3587;%%

\bibitem{Airapetian:2009bi} 
  Airapetian A {\it et al.}  [HERMES Collaboration] 2010
  Nuclear-mass dependence of azimuthal beam-helicity and beam-charge asymmetries in deeply virtual Compton scattering
  {\it Phys.\ Rev.\ C} {\bf 81}, 035202
  %[arXiv:0911.0091 [hep-ex]].
%\cite{Airapetian:2012pg}

\bibitem{solid_pcdr} 
  SoLID Collaboration, ``Solenoial Large Intensity Device Preliminary Conceptual Design Report,''
  $http://hallaweb.jlab.org/12GeV/SoLID/files/solid\_precdr.pdf$

\bibitem{e12-10-006} 
  ``Target Single Spin Asymmetry in Semi-Inclusive Deep-Inelastic (e,e'$\pi^{\pm}$) Reaction on a Transversely Polarized $^{3}He$ Target at 11~GeV'',
$http://hallaweb.jlab.org/collab/PAC/PAC34/PR-09-014-transversity.pdf$

%\cite{Defurne:2015kxq}
\bibitem{Defurne:2015kxq} 
  M.~Defurne {\it et al.}  [Hall A Collaboration],
  %``The E00-110 experiment in Jefferson Lab's Hall A: Deeply Virtual Compton Scattering off the Proton at 6 GeV,''
  arXiv:1504.05453 [nucl-ex].
  %%CITATION = ARXIV:1504.05453;%%
%\cite{Jo:2015ema}
\bibitem{Jo:2015ema} 
  H.~S.~Jo {\it et al.}  [CLAS Collaboration],
  %``Cross sections for the exclusive photon electroproduction on the proton and Generalized Parton Distributions,''
  arXiv:1504.02009 [hep-ex].
  %%CITATION = ARXIV:1504.02009;%%
%\cite{Mueller:1998fv}
